---
title: "codingRMD_MNK"
author: "MNK"
date: "`r Sys.Date()`"
output:
  pdf_document:
      toc: true
      toc_depth: 3
      number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Packages
```{r packages, message=FALSE, warning=FALSE}
if(!requireNamespace("haven")) install.packages("haven"); library(haven)
if(!requireNamespace("dplyr")) install.packages("dplyr"); library(dplyr)
if(!requireNamespace("visdat")) install.packages("visdat"); library(visdat)
if(!requireNamespace("naniar")) install.packages("naniar"); library(naniar)
if(!requireNamespace("psych")) install.packages("psych"); library(psych)
if(!requireNamespace("mice")) install.packages("mice"); library(mice)
if(!requireNamespace("Hmisc")) install.packages("Hmisc"); library(Hmisc)
if(!requireNamespace("knitr")) install.packages("knitr"); library(knitr)
if(!requireNamespace("kableExtra")) install.packages("kableExtra"); library(kableExtra)
if(!requireNamespace("lavaan")) install.packages("lavaan"); library(lavaan)

```

# Loading files (and predefined transformation)
## EMC data
```{r EMC data loading}
setwd("V:/Research/Dementie/Studenten/Studenten/Max/Databeheer")

dataEMC <- haven::read_sav("data_SCTQ_merged_16072024.sav") #load EMC collected data
dataEMC[dataEMC == 999] <- NA

dataEMC_copy <- dataEMC
```

## UMCG data
```{r UMCG data loading}
setwd("V:/Research/Dementie/Studenten/Studenten/Max/Databeheer")
dataUMCG <- haven::read_sav("data_SC_UMCG_mnk.sav") #load UMCG collected data
dataUMCG[dataUMCG == 999] <- NA

dataUMCG_copy <- dataUMCG
```

# Data preprocessing
## Pre defined transformation
```{r}
dataEMC$TAS20_fac1_tf <- 35 - dataEMC$TAS20_fac1_Identificeren_Gevoelens
dataUMCG$TAS20_fac1_tf <- 35 - dataUMCG$TAS20_fac1_Identificeren_Gevoelens
```

## Synchronizing names and compute totals
```{r}
dataEMC$FP_1_6_total <- dataEMC$FP_1t6_ToM + dataEMC$FP_1t6_empathy
colnames(dataUMCG)[which(colnames(dataUMCG) == "SET_UMCG_Totaal")] <- "SET_UMCG_total"
dataEMC$SET_UMCG_Cognitief_Totaal <- dataEMC$SET_UMCG_1 +dataEMC$SET_UMCG_2 + dataEMC$SET_UMCG_3
dataEMC$SET_UMCG_Affectief_Totaal <- dataEMC$SET_UMCG_4 +dataEMC$SET_UMCG_5 + dataEMC$SET_UMCG_6
```

## Creating ID values for UMCG sample
```{r}
dataUMCG$ID <- paste0("UMCG", seq(1, nrow(dataUMCG)))
```


## Data pooling
```{r data pooling, warning=FALSE}
data_pooled <- dplyr::bind_rows(dataEMC, dataUMCG) # pooling the data
data_pooled_copy <- data_pooled
```

## Renaming and var name sets
```{r Data preprocessing}
names_relevant_items <- c("Ekman60_total", "ERT_total", "TAS20_fac1_tf", 
                          "FP_1_6_total", "hintingtask_total", "cartoons_total", "SET_total_mc", "SET_UMCG_total", 
                          "SNQ_NL_total", "RSMS_AMSP", "MBI_total")
names_rel_items_abbr <- c('EKM60t', 'ERTt', 'TASf1', 
                          'FP_Gt', 'HT_Gt', 'CART_Gt', 'SETt', 'SET_Gt',
                          'SNQt', 'RSMSf1', 'MBIt')
names(data_pooled)[match(names_relevant_items, names(data_pooled))] <- names_rel_items_abbr #renaming
names_covariates <- c("age", "sex", "education_level")
```

## Missing values part 1; visualisation
```{r}
vis_miss(data_pooled[,names_rel_items_abbr])
```

In the above plot it is visible that we miss >=63% of data for four items (ERT, SET, RSMS, MBI). These items were not included in the data collection of UMCG, and therefor we assume that these missing values are missing completely at random (aka the characteristics of these participants did not influence whether this data is present/absent). Data for the UMCH sample will be imputed for those four items using stochastic imputation based the two variables that have the highest and significant correlations with the items.

15% of data is missing for SET_Gt, all these missings are in the EMC data. For those people, SET was conducted with another testing protocol (solely multiple choise question, no open questions). We will impute SET_Gt scores for these people based on means in the EMC sample corrected for their scores on the MC questions.

The 8% missing values for the CART_Gt variable can probably be explained by lack of time (slower participants) because it was the last test in the EMC protocol. We will impute the scores using stochastic imputation based on th two variables that have the highest and significant correlation with this test.

Imputation will be continued after checks for outliers and non-normality.

# Data checks
## EMC sample data checks
Descriptes before outlier deletion and/or tranformations
```{r}
# Descriptives EMC start
psych::describe(data_pooled[data_pooled$centerID == "EMC", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(n, min, max, mean, median, sd, skew, kurtosis)
```

### Outliers - EMC
```{r}
dataEMC_subset_scaled <- cbind(data_pooled[data_pooled$centerID == "EMC",][, c("ID", names_covariates, "MoCA_total")], scale(data_pooled[data_pooled$centerID == "EMC",][,names_rel_items_abbr]))
moca_below26_EMC <- dataEMC_subset_scaled$MoCA_total < 26

outlierCheck_EMC <- data.frame(cbind(moca_below26_EMC, abs(dataEMC_subset_scaled[,names_rel_items_abbr])>3))
#outlierCheck_EMC <- cbind(moca_below26_EMC, sapply(dataEMC_subset_scaled[,names_rel_items_abbr], FUN = function(x) abs(x)>3))

rowSums(outlierCheck_EMC, na.rm = TRUE)

meanitemSS_EMC <- rowMeans(dataEMC_subset_scaled[,c(
                          'EKM60t', 'ERTt', 'TASf1', 
                          'FP_Gt', 'CART_Gt', 'SETt',
                          'SNQt', 'RSMSf1', 'MBIt')], na.rm = TRUE)
SSmeanitemSS_EMC <- scale(meanitemSS_EMC)
outlier_EMC <- dataEMC_subset_scaled[which(abs(SSmeanitemSS_EMC)>3), "ID"]
length(outlier_EMC)
```
We have one participant that has an absolute scaled mean item scaled score of over 3, we will exclude this participant from analyses.

```{r}
data_pooled <- data_pooled[-(which(data_pooled$ID==outlier_EMC)),]
```

### Normality - EMC
```{r}
psych::describe(data_pooled[data_pooled$centerID == "EMC", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(n, min, max, mean, median, sd, skew, kurtosis)

normalityCheck_EMC <- psych::describe(data_pooled[data_pooled$centerID == "EMC", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(skew, kurtosis)

any(abs(normalityCheck_EMC$skew)>3)
any(abs(normalityCheck_EMC$kurtosis)>10)
```
No absolute skew>3 and no absolute kurtosis>10 is EMC sample after deleting 1 outlier.


### Imputing the SET_Gt variable some EMC missings due to different testing protocol
```{r imputation SET_Gt for EMC missings}
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_2), "SET_open_2"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_2"], na.rm = TRUE))
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_3), "SET_open_3"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_3"], na.rm = TRUE))
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_6), "SET_open_6"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_6"], na.rm = TRUE))
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_14), "SET_open_14"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_14"], na.rm = TRUE))
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_16), "SET_open_16"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_16"], na.rm = TRUE))
data_pooled[data_pooled$centerID == "EMC" & is.na(data_pooled$SET_open_17), "SET_open_17"] <- 
  as.numeric(colMeans(data_pooled[data_pooled$centerID == "EMC", "SET_open_17"], na.rm = TRUE))

data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_1"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_2 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_2
data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_2"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_3 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_3
data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_3"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_6 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_6
data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_4"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_14 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_14
data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_5"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_16 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_16
data_pooled[data_pooled$centerID == "EMC", "SET_UMCG_6"] <- 
  data_pooled[data_pooled$centerID == "EMC",]$SET_open_17 + data_pooled[data_pooled$centerID == "EMC",]$SET_mc_17

data_pooled$SET_Gt <- rowSums(data_pooled[,c(which(names(data_pooled)=="SET_UMCG_1") : which(names(data_pooled)=="SET_UMCG_6"))])
```


## UMCG sample data checks
Descriptives before outlier deletion and/or tranformations
```{r, warning=FALSE, message=FALSE}
# Descriptives UMCG start
psych::describe(data_pooled[data_pooled$centerID == "UMCG", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(n, min, max, mean, median, sd, skew, kurtosis)
```

### Outliers - UMCG
```{r}
dataUMCG_subset_scaled <- cbind(data_pooled[data_pooled$centerID == "UMCG",][, c("ID", names_covariates, "MoCA_total")], scale(data_pooled[data_pooled$centerID == "UMCG",][,names_rel_items_abbr]))
moca_below26_UMCG <- dataUMCG_subset_scaled$MoCA_total < 26

outlierCheck_UMCG <- data.frame(cbind(moca_below26_UMCG, abs(dataUMCG_subset_scaled[,names_rel_items_abbr])>3))
#outlierCheck_UMCG <- cbind(moca_below26_UMCG, sapply(dataUMCG_subset_scaled[,names_rel_items_abbr], FUN = function(x) abs(x)>3))

rowSums(outlierCheck_UMCG, na.rm = TRUE)

meanitemSS_UMCG <- rowMeans(dataUMCG_subset_scaled[,c(
                          'EKM60t', 'ERTt', 'TASf1', 
                          'FP_Gt', 'CART_Gt', 'SET_Gt',
                          'SNQt', 'RSMSf1', 'MBIt')], na.rm = TRUE)
SSmeanitemSS_UMCG <- scale(meanitemSS_UMCG)
outlier_UMCG <- dataUMCG_subset_scaled[which(abs(SSmeanitemSS_UMCG)>3), "ID"]
length(outlier_UMCG)
```
We have one participant that has an absolute scaled mean item scaled score of over 3, we will exclude this participant from analyses.

```{r}
data_pooled <- data_pooled[-(which(data_pooled$ID==outlier_UMCG)),]
```

### Normality - UMCG
```{r, warning=FALSE, message=FALSE}
psych::describe(data_pooled[data_pooled$centerID == "UMCG", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(n, min, max, mean, median, sd, skew, kurtosis)

normalityCheck_UMCG <- psych::describe(data_pooled[data_pooled$centerID == "UMCG", c(names_covariates, "MoCA_total", names_rel_items_abbr)]) %>%
  select(skew, kurtosis)

any(abs(normalityCheck_UMCG$skew)>3, na.rm = TRUE)
any(abs(normalityCheck_UMCG$kurtosis)>10, na.rm = TRUE)
```
No absolute skew>3 and no absolute kurtosis>10 is EMC sample after deleting 1 outlier.



# Stochastic imputation
At this point, we have the following missing values.
```{r}
vis_miss(data_pooled[,c("age", "education_level",names_rel_items_abbr)])
```
And the following zero order paired correlation (respectively: corr, N, p-values).

```{r}
rcorr(as.matrix(data_pooled[, c("age", "education_level", 
                                        'EKM60t', 'ERTt', 'TASf1', 
                                        'FP_Gt', 'CART_Gt', 'SET_Gt',
                                        'SNQt', 'RSMSf1', 'MBIt')]))
```

## Imputation predictor selection
### Predictor selection ERTt
Lets check the correlations of ERTt with other relevant variables.

```{r}
matcor <- Hmisc:: rcorr(as.matrix(data_pooled[, c("age", "education_level", 
                                        'EKM60t', 'ERTt', 'TASf1', 
                                        'FP_Gt', 'HT_Gt', 'CART_Gt', 'SET_Gt',
                                        'SNQt', 'RSMSf1', 'MBIt')]))

#Check whether sex is also a significant predictor
sexERTt <- lm(ERTt ~ sex, data = data_pooled)
summary(sexERTt)$coefficients["sex", "Pr(>|t|)"] #Not significant

sigpred_ERTt <- matcor$r["ERTt",matcor$P["ERTt",]<.05]; sigpred_ERTt #significant correlations of ERTt

# corrplot(matcor$r, p.mat = matcor$P, sig.level = 0.05, method = "number", type = "lower", tl.col = "black", tl.srt = 45,
#          #insig = "blank", 
#          addCoef.col = "black")
```

We will impute the missing ERTt values using predictive mean matching (stochastic) based on the significant predictors.


### Predictor selection RSMSf1
Lets check the correlations of RSMSf1 with other relevant variables.

```{r}
#Check whether sex is also a significant predictor
sexRSMSf1 <- lm(RSMSf1 ~ sex, data = data_pooled)
summary(sexRSMSf1)$coefficients["sex", "Pr(>|t|)"] #Not significant

#Check numerical correlations
sigpred_RSMSf1 <- matcor$r["RSMSf1",matcor$P["RSMSf1",]<.05]; sigpred_RSMSf1 #significant correlations of RSMSf1
```

### Predictor selection MBIt
Lets check the correlations of MBIt with other relevant variables.

```{r}
#Check whether sex is also a significant predictor
sexMBIt <- lm(MBIt ~ sex, data = data_pooled)
summary(sexMBIt)$coefficients["sex", "Pr(>|t|)"] #Not significant

#Check numerical correlations
sigpred_MBIt <- matcor$r["MBIt",matcor$P["MBIt",]<.05]; sigpred_MBIt #significant correlations of MBIt
```


## Imputation of ERTt, RSMSf, MBIt
```{r}
data_pooled_subset <- data_pooled[,c("ID", "centerID", "sex", "age", "education_level", 
                                        'EKM60t', 'ERTt', 'TASf1', 
                                        'FP_Gt', 'CART_Gt', 'SET_Gt',
                                        'SNQt', 'RSMSf1', 'MBIt')]

predictor_matrix <- make.predictorMatrix(data_pooled_subset)
predictor_matrix[] <- 0

#assign the significant predictors to the prediction matrix
predictor_matrix["ERTt", ] <- colnames(predictor_matrix) %in% names(sigpred_ERTt)[!is.na(names(sigpred_ERTt))]
predictor_matrix["RSMSf1", ] <- colnames(predictor_matrix) %in% names(sigpred_RSMSf1)[!is.na(names(sigpred_RSMSf1))]
predictor_matrix["MBIt", ] <- colnames(predictor_matrix) %in% names(sigpred_MBIt)[!is.na(names(sigpred_MBIt))]

#assign imputation medhods
imputation_methods <- make.method(data_pooled_subset)
imputation_methods[] <- ""  # Set all methods to "" initially
imputation_methods[c("ERTt", "RSMSf1", "MBIt")] <- "pmm"  # Use "pmm" for ERTt

#imputation
data_pooled_subset_imp <- complete(mice(data_pooled_subset, 
                               method = imputation_methods, 
                               predictorMatrix = predictor_matrix, 
                               m = 1, 
                               seed = 42), 1)
```

### Visualisation ERTt impuations
```{r}
# Stochastic regression imputation plot for ERTt
plot(data_pooled_subset$EKM60t[!is.na(data_pooled_subset$ERTt)], data_pooled_subset_imp$ERTt[!is.na(data_pooled_subset$ERTt)],# Plot of observed values
     main = "Stochastic Regression",
     xlab = "EKMt", ylab = "ERTt")
points(data_pooled_subset$EKM60t[is.na(data_pooled_subset$ERTt)], data_pooled_subset_imp$ERTt[is.na(data_pooled_subset$ERTt)],# Plot of missing values
       col = "red")
abline(lm(data_pooled_subset$ERTt ~ data_pooled_subset$EKM60t, data_pooled_subset_imp), col = "#1b98e0", lwd = 1.5) # Regression slope
```


### Visualisation RSMSf1 impuations
```{r}
# Stochastic regression imputation plot for RSMSf1
plot(data_pooled_subset$TASf1[!is.na(data_pooled_subset$RSMSf1)], data_pooled_subset_imp$RSMSf1[!is.na(data_pooled_subset$RSMSf1)],# Plot of observed values
     main = "Stochastic Regression",
     xlab = "TASf1", ylab = "RSMSf1")
points(data_pooled_subset$TASf1[is.na(data_pooled_subset$RSMSf1)], data_pooled_subset_imp$RSMSf1[is.na(data_pooled_subset$RSMSf1)],# Plot of missing values
       col = "red")
abline(lm(data_pooled_subset$RSMSf1 ~ data_pooled_subset$TASf1, data_pooled_subset_imp), col = "#1b98e0", lwd = 1.5) # Regression slope
```

### Visualisation MBIt impuations
```{r}
# Stochastic regression imputation plot for MBIt
plot(data_pooled_subset$age[!is.na(data_pooled_subset$MBIt)], data_pooled_subset_imp$MBIt[!is.na(data_pooled_subset$MBIt)],# Plot of observed values
     main = "Stochastic Regression",
     xlab = "age", ylab = "MBIt")
points(data_pooled_subset$age[is.na(data_pooled_subset$MBIt)], data_pooled_subset_imp$MBIt[is.na(data_pooled_subset$MBIt)],# Plot of missing values
       col = "red")
abline(lm(data_pooled_subset$MBIt ~ data_pooled_subset$age, data_pooled_subset_imp), col = "#1b98e0", lwd = 1.5) # Regression slope

```

## Mid term missing data evaluation
At this point, we have the following missing data:
```{r}
vis_miss(data_pooled_subset_imp[,-1])
```
We will impute the remaining missing values, again with a stochastic approach based on significant correlations or significant t.test for sex.

## Imputation predictor selection part 2
### Predictor selection CART_Gt
Lets check the correlations of CART_Gt with other relevant variables.

```{r}
matcor2 <- Hmisc:: rcorr(as.matrix(data_pooled_subset_imp[, c("age", "education_level", 
                                        'EKM60t', 'ERTt', 'TASf1', 
                                        'FP_Gt', 'CART_Gt', 'SET_Gt',
                                        'SNQt', 'RSMSf1', 'MBIt')]))

#Check whether sex is also a significant predictor
sexCART_Gt <- lm(CART_Gt ~ sex, data = data_pooled_subset_imp)
summary(sexCART_Gt)$coefficients["sex", "Pr(>|t|)"] #Significant

sigpred_CART_Gt <- matcor2$r["CART_Gt",matcor2$P["CART_Gt",]<.05]; sigpred_CART_Gt #significant correlations of CART_Gt
sigpred_CART_Gt$sex <- summary(sexCART_Gt)$coefficients["sex", "Pr(>|t|)"] #Significant

```

### Predictor selection SET_Gt
Lets check the correlations of SET_Gt with other relevant variables.

```{r}

#Check whether sex is also a significant predictor
sexSET_Gt <- lm(SET_Gt ~ sex, data = data_pooled_subset_imp)
summary(sexSET_Gt)$coefficients["sex", "Pr(>|t|)"] #Not ignificant

sigpred_SET_Gt <- matcor2$r["SET_Gt",matcor2$P["SET_Gt",]<.05]; sigpred_SET_Gt #significant correlations of SET_Gt
```

### Predictor selection EKM60t
Lets check the correlations of EKM60t with other relevant variables.

```{r}
#Check whether sex is also a significant predictor
sexEKM60t <- lm(EKM60t ~ sex, data = data_pooled_subset_imp)
summary(sexEKM60t)$coefficients["sex", "Pr(>|t|)"] #Not significant

sigpred_EKM60t <- matcor2$r["EKM60t",matcor2$P["EKM60t",]<.05]; sigpred_EKM60t #significant correlations of EKM60t
```


### Predictor selection ERTt (second round)
Lets check the correlations of ERTt with other relevant variables.

```{r}
#Check whether sex is also a significant predictor
sexERTt_2nd <- lm(ERTt ~ sex, data = data_pooled_subset_imp)
summary(sexERTt_2nd)$coefficients["sex", "Pr(>|t|)"] #Not significant

sigpred_ERTt_2nd <- matcor2$r["ERTt",matcor2$P["ERTt",]<.05]; sigpred_ERTt_2nd #significant correlations of ERTt
```


## Imputation of CART_Gt, SET_Gt, EKM60t, ERTt (2nd imputation round)
```{r}
data_pooled_subset_imp2 <- data_pooled_subset_imp

predictor_matrix2 <- make.predictorMatrix(data_pooled_subset_imp)
predictor_matrix2[] <- 0

#assign the significant predictors to the prediction matrix
predictor_matrix2["CART_Gt", ] <- 
  colnames(predictor_matrix2) %in% names(sigpred_CART_Gt)[!is.na(names(sigpred_CART_Gt))]
predictor_matrix2["SET_Gt", ] <- 
  colnames(predictor_matrix2) %in% names(sigpred_SET_Gt)[!is.na(names(sigpred_SET_Gt))]
predictor_matrix2["EKM60t", ] <- 
  colnames(predictor_matrix2) %in% names(sigpred_EKM60t)[!is.na(names(sigpred_EKM60t))]
predictor_matrix2["ERTt", ] <- 
  colnames(predictor_matrix2) %in% names(sigpred_ERTt_2nd)[!is.na(names(sigpred_ERTt_2nd))]


#assign imputation medhods
imputation_methods2 <- make.method(data_pooled_subset_imp)
imputation_methods2[] <- ""  # Set all methods to "" initially
imputation_methods2[c("CART_Gt", "SET_Gt", "EKM60t", "ERTt")] <- "pmm"  # Use "pmm" for ERTt

#imputation
data_pooled_subset_imp2 <- complete(mice(data_pooled_subset_imp, 
                               method = imputation_methods2, 
                               predictorMatrix = predictor_matrix2, 
                               m = 1, 
                               seed = 42), 1)
```

### Check after imputation part 2
```{r}
vis_miss(data_pooled_subset_imp2)
```

No missing values anymore


# Final dataset
## Characteristics
```{r}
data_final <- data_pooled_subset_imp2

descriptives_data_final <- psych::describe(data_final[,-1]) %>%
  select(n, min, max, mean, median, sd, skew, kurtosis); descriptives_data_final

corr_data_final <- Hmisc:: rcorr(as.matrix(data_final[,-c(1:2)])); corr_data_final
corr_data_final_r <- round(as.data.frame(corr_data_final$r), 3); corr_data_final_r
corr_data_final_P <- round(as.data.frame(corr_data_final$P), 3); corr_data_final_P

#knitr::kable(corr_data_final_r, format = "latex", booktabs = TRUE, caption = "Correlation matrix final dataset")
#knitr::kable(corr_data_final_P, format = "latex", booktabs = TRUE, caption = "P-values corresponding to the correlations")
```

## Z-scores
```{r}
names_items_analysis <- c("EKM60t", "ERTt", "TASf1", "CART_Gt", "FP_Gt", "SET_Gt", "SNQt", "MBIt", "RSMSf1")
data_final_Z <- cbind(data_final[, c("ID", "centerID", names_covariates)], round(scale(data_final[, names_items_analysis]), 4))
```


# Analyses 
## CFA models
```{r}
#full 3 factor model
m1_f3fm <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Allow factors to be correlated
f1_P ~~ f2_U
f1_P ~~ f3_BR
f2_U ~~ f3_BR
'

#two factor model: f1 = f2
m2_2fm_1eq2 <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Allow factors to be correlated
f1_P ~~ 1*f2_U  # Fix correlation between f1_P and f2_U at 1
f1_P ~~ f3_BR
f2_U ~~ f3_BR
'

#model 3: two factor model: f1 = f3 (CART)
m3_2fm_1eq3 <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Allow factors to be correlated
f1_P ~~ f2_U  
f1_P ~~ 1*f3_BR # Fix correlation between f1_P and f3_BR at 1
f2_U ~~ f3_BR
'

#model 4: two factor model: f2 = f3 (CART)
m4_2fm_2eq3 <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Allow factors to be correlated
f1_P ~~ f2_U  
f1_P ~~ f3_BR 
f2_U ~~ 1*f3_BR # Fix correlation between f2_U and f3_BR at 1
'

#model 5: one factor model: f1 = f2 = f3 (CART)
m5_1fm <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Fixing all interfactor correlations at 1
f1_P ~~ 1*f2_U
f1_P ~~ 1*f3_BR
f2_U ~~ 1*f3_BR
'

#model 6: 3 one factor model: independent factors (CART)
m6_3x1fm <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Fixing all interfactor correlations at 0
f1_P ~~ 0*f2_U
f1_P ~~ 0*f3_BR
f2_U ~~ 0*f3_BR
'

 #model 6.3alt: 3 factor model; BR independent
m6_3fm_BRindep <- '
# Defining the factors (latent variables)
f1_P =~ EKM60t + ERTt + TASf1
f2_U =~ SET_Gt + FP_Gt + CART_Gt
f3_BR =~ RSMSf1 + SNQt + MBIt

# Fixing all interfactor correlations at 0
f1_P ~~ f2_U
f1_P ~~ 0*f3_BR
f2_U ~~ 0*f3_BR
'
```


## CFA EMC data (N=47)
```{r}
#model 1; EMC data
fit_m1_EMC <- cfa(model = m1_f3fm, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m1_EMC <- summary(fit_m1_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m1_EMC <- fitMeasures(fit_m1_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 2; EMC data
fit_m2_EMC <- cfa(model = m2_2fm_1eq2, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m2_EMC <- summary(fit_m2_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m2_EMC <- fitMeasures(fit_m2_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 3; EMC data
fit_m3_EMC <- cfa(model = m3_2fm_1eq3, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m3_EMC <- summary(fit_m3_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m3_EMC <- fitMeasures(fit_m3_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 4; EMC data
fit_m4_EMC <- cfa(model = m4_2fm_2eq3, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m4_EMC <- summary(fit_m4_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m4_EMC <- fitMeasures(fit_m4_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 5; EMC data
fit_m5_EMC <- cfa(model = m5_1fm, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m5_EMC <- summary(fit_m5_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m5_EMC <- fitMeasures(fit_m5_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
# #model 6; EMC data
# fit_m6_EMC <- cfa(model = m6_3x1fm, data = data_final_Z[data_final_Z$centerID == "EMC",])
# summ_m6_EMC <- summary(fit_m6_EMC, standardized = TRUE, fit.measures = TRUE)
# fm_m6_EMC <- fitMeasures(fit_m6_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```

```{r}
#model 6.3; EMC data
fit_m6.3alt_EMC <- cfa(model = m6_3fm_BRindep, data = data_final_Z[data_final_Z$centerID == "EMC",])
summ_m6.3alt_EMC <- summary(fit_m6.3alt_EMC, standardized = TRUE, fit.measures = TRUE)
fm_m6.3alt_EMC <- fitMeasures(fit_m6.3alt_EMC, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```


## CFA pooled data (N=128)
```{r}
#model 1; pooled data
fit_m1_pld <- cfa(model = m1_f3fm, data = data_final_Z)
summ_m1_pld <- summary(fit_m1_pld, standardized = TRUE, fit.measures = TRUE)
fm_m1_pld <- fitMeasures(fit_m1_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 2; pooled data
fit_m2_pld <- cfa(model = m2_2fm_1eq2, data = data_final_Z)
summ_m2_pld <- summary(fit_m2_pld, standardized = TRUE, fit.measures = TRUE)
fm_m2_pld <- fitMeasures(fit_m2_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 3; pooled data
fit_m3_pld <- cfa(model = m3_2fm_1eq3, data = data_final_Z)
summ_m3_pld <- summary(fit_m3_pld, standardized = TRUE, fit.measures = TRUE)
fm_m3_pld <- fitMeasures(fit_m3_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 4; pooled data
fit_m4_pld <- cfa(model = m4_2fm_2eq3, data = data_final_Z)
summ_m4_pld <- summary(fit_m4_pld, standardized = TRUE, fit.measures = TRUE)
fm_m4_pld <- fitMeasures(fit_m4_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 5; pooled data
fit_m5_pld <- cfa(model = m5_1fm, data = data_final_Z)
summ_m5_pld <- summary(fit_m5_pld, standardized = TRUE, fit.measures = TRUE)
fm_m5_pld <- fitMeasures(fit_m5_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```
```{r}
#model 6; pooled data
fit_m6_pld <- cfa(model = m6_3x1fm, data = data_final_Z)
summ_m6_pld <- summary(fit_m6_pld, standardized = TRUE, fit.measures = TRUE)
fm_m6_pld <- fitMeasures(fit_m6_pld, c("npar", "chisq", "df", "pvalue", "aic", "srmr", "cfi", "ifi", "nfi", "rmsea", "bic"))
```




## SEM models

## SEM EMC data (N=47)

# Results
## CFA EMC data
### Fit indices
```{r}
results_CFA_EMC <- data.frame(round(rbind(fm_m1_EMC, fm_m2_EMC, fm_m3_EMC, fm_m4_EMC, fm_m5_EMC
                                          #, fm_m6_EMC
                                          ), 3))
modelNames_CFA <- c("Full three-factor", "Two-factor: P = U", "Two-factor: P = BR", "Two-factor: U = BR", "One-factor: P = U = BR"
                    #, "Independent three factor"
                    )
rownames(results_CFA_EMC) <- NULL
results_CFA_EMC <- cbind(Model = modelNames_CFA, results_CFA_EMC)
results_CFA_EMC
results_CFA_EMC[,c("Model", "npar", "df", "chisq", "pvalue", "aic", "bic", "srmr", "cfi", "ifi")]
```
### Model comparisson
```{r}
anova(fit_m1_EMC, fit_m2_EMC)
anova(fit_m1_EMC, fit_m3_EMC)
anova(fit_m1_EMC, fit_m4_EMC)
anova(fit_m1_EMC, fit_m5_EMC)
#anova(fit_m1_EMC, fit_m6_EMC)
```

### Favoured model
```{r}
est_par_CFA_EMC <- parameterEstimates(fit_m1_EMC, standardized = TRUE)
rownames(est_par_CFA_EMC) <- NULL
est_par_CFA_EMC
```


## CFA pooled data
### Fit indices
```{r}
results_CFA_pld <- data.frame(round(rbind(fm_m1_pld, fm_m2_pld, fm_m3_pld, fm_m4_pld, fm_m5_pld, fm_m6_pld), 3))
modelNames_CFA <- c("Full three-factor", "Two-factor: P = U", "Two-factor: P = BR", "Two-factor: U = BR", "One-factor: P = U = BR", "Independent three factor")
rownames(results_CFA_pld) <- NULL
results_CFA_pld <- cbind(Model = modelNames_CFA, results_CFA_pld)
results_CFA_pld
```
### Model comparisson
```{r}
anova(fit_m1_pld, fit_m2_pld)
anova(fit_m1_pld, fit_m3_pld)
anova(fit_m1_pld, fit_m4_pld)
anova(fit_m1_pld, fit_m5_pld)
anova(fit_m1_pld, fit_m6_pld)
```

```{r}
# anova(fit_m2_pld, fit_m5_pld)
# anova(fit_m3_pld, fit_m5_pld)
# anova(fit_m4_pld, fit_m5_pld)
```

### Favoured model
```{r}
est_par_CFA_pld <- parameterEstimates(fit_m1_pld, standardized = TRUE)
rownames(est_par_CFA_pld) <- NULL
est_par_CFA_pld
```

